Fusion Moves for Correlation Clustering

### 2014-11-14 paper/egpaper_for_review.tex
fixed all changes including page 4 for which i knew the fix

The choice of the proposal defines the shape of the inner polytope. 
In the given toy example, the first (red) polytope give a huge improvement, the second proposal
defines the blue polytope which does not lead to an improvement. 
The third proposal generates the green polytope that includes the global optimal solution.

This procedure is fundamental different to common polyhedral multicut methods~\cite{kappes_2011_emmcvpr,kappes_2013_arxiv}, 
which tighten a outer relaxation of the multicut polytope and contrary to our method do not operate in the feasible domain.

@@

A proposal have a high quality if it at least in some regions have a low energy.
For high quality proposals the chance that the inner polytope includes 
better solution (vertex) is larger than for those with low quality.

Diversity between the individual proposals increase the chances
to span diverse internal polytopes, cover with the intersection of
inner polytopes a large part of the original polytope and find 
more likely the global optimal solution or escape from local minima.

@@

\noindent \textbf{Randomized HierarchicalClustering (RHC):}
%\subsubsection{Randomized HierarchicalClustering (RHC)}
%
To generate fast energy aware proposals we can use energy
based hierarchical clustering (EHC) as defined in Sec.~\ref{sec:ehc}.
EHC follows the energy function, therefore the \emph{quality}
of the proposals is high.
To get \emph{diversity} among the different proposal,
we add normal distributed noise  $\mathcal{N}(0, \sigma_{ehc})$
to each edge weight.
To get proposals of the desired \emph{size}, we use a
different stop condition as in EHC, and stop iff a certain number of connected
components is reached.

>>>>

The choice of the proposal defines the shape of the inner polytope. 
In the given toy example, the first (red) polytope give a huge improvement, the second proposal
defines the blue polytope which does not lead to an improvement. 
The third proposal generates the green polytope that includes the globally optimal solution.

This procedure is fundamentally different from common polyhedral multicut methods~\cite{kappes_2011_emmcvpr,kappes_2013_arxiv}, 
which tighten an outer relaxation of the multicut polytope and contrary to our method do not operate in the feasible domain.

@@

A proposal has a high quality if it at least in some regions has a low energy.
For high quality proposals the chance that the inner polytope includes a
better solution (vertex) is larger than for those with low quality.

Diversity between the individual proposals increases the chances
to span diverse internal polytopes, cover with the intersection of
inner polytopes a large part of the original polytope and find 
more likely the global optimal solution or escape from local minima.

@@

\noindent \textbf{Randomized HierarchicalClustering (RHC):}
%\subsubsection{Randomized HierarchicalClustering (RHC)}
%
To generate fast energy aware proposals we can use energy
based hierarchical clustering (EHC) as defined in Sec.~\ref{sec:ehc}.
EHC follows the energy function, therefore the \emph{quality}
of the proposals is high.
To get \emph{diversity} among the different proposal,
we add normally distributed noise  $\mathcal{N}(0, \sigma_{ehc})$
to each edge weight.
To get proposals of the desired \emph{size}, we use a
different stop condition as in EHC, and stop iff a certain number of connected
components is reached.
